---
title: "R Concept Walkthrough"
---

# Using Functions in R: Beginner Walk-through

A function is a block of code in R that performs a specific task. Functions take one or more input arguments, perform operations on those arguments, and return a result. In R, you can use built-in functions, as well as create your own custom functions.

## **How to create a function in R**

To create a function in R, you use the **`function()`** keyword, followed by the function name and the input values in parentheses. Here is an example of a simple function that takes two values, adds them together, and returns the result:

```{r}
Flannery_sum <- function(x, y) {
  z <- x + y
  return(z)
}
```

In this example, my_sum is the name of the function, and x and y are the input arguments. The function performs the addition operation z \<- x + y and returns the result z.

Then, to use this function, you use 2 numbers as input argument and then get the result:

```{r}
Flannery_sum(2, 3)

```

You can also use the **`mean()`** function to calculate the average of a set of numbers.

For example:

```{r}
numbers <- c(2, 4, 6, 8, 10)
mean(numbers)
```

This function will result in **`6`**, because **`(2 + 4 + 6 + 8 + 10) / 5 = 6`**.

...

You can also modify the function to return a sentence about the equation instead of just the result:

```{r}
Flannery_sum <- function(x, y) {
  z <- x + y
  sentence <- paste("The sum of", x, "and", y, "is", z)
  return(sentence)
}
```

In this example, the **`Flannery_sum`** function takes two input arguments, **`x`** and **`y`**, and calculates their sum. It then creates a sentence using the **`paste()`** function, which joins the input variables and strings them together.

You can still use numbers as input variables to get the result:

```{r}
Flannery_sum(2, 3)
```

You can also use the **`paste()`** function to make sentences. An example of how you can use the **`paste()`** function to create a sentence is:

```{r}
fruit1 <- "apples"
fruit2 <- "bananas"
Flannerypreference <- paste("I prefer to eat", fruit1, "and", fruit2)

```

In this example, I used the **`paste()`** function to join four separate parts of the eventual sentence together: **`"I prefer to eat"`**, the value of the **`fruit1`** variable, **`"and"`**, and the value of the **`fruit2`** variable.

Therefore, using the next line of code below, the sentence is formed.

```{r}
print(Flannerypreference)

```
