---
title: "R Concept Walkthrough"
---

# Using Functions in R: Beginner Walk-through

A function is a block of code in R that performs a specific task. Functions take one or more input arguments, perform operations on those arguments, and return a result. In R, you can use built-in functions, as well as create your own custom functions.

## **How to create a function in R**

To create a function in R, you use the **`function()`** keyword, followed by the function name and the input values in parentheses. Here is an example of a simple function that takes two values, adds them together, and returns the result:

```{r}
Flannery_sum <- function(x, y) {
  z <- x + y
  return(z)
}
```

In this example, my_sum is the name of the function, and x and y are the input arguments. The function performs the addition operation z \<- x + y and returns the result z.

Then, to use this function, you use 2 numbers as input argument and then get the result:

```{r}
Flannery_sum(2, 3)

```

You can also use the **`mean()`** function to calculate the average of a set of numbers.

For example:

```{r}
numbers <- c(2, 4, 6, 8, 10)
mean(numbers)
```

This function will result in **`6`**, since **`(2 + 4 + 6 + 8 + 10) / 5 = 6`**.
